

Table~\ref{tab:pcr-effects} shows the measured effects of treatments with IL-1$\beta$ and Wnt-3a
on the expression of some proteins in chondrocyte donor cells.
The table shows that both cytokines cause effects on the measured protein concentrations. Moreover,
the combined action of the two treatments is not always the sum of the
two isolated cases (see for example Sox9 and ColIIa).
Finally, the transcriptional response to the treatments may vary over time (see the case of ColIIa
under Wnt-3a treatment, and experimental data in Suppl. Mat.).
From this we infer that the signaling pathways of IL-1$\beta$ and Wnt-3a have some common
parts, possibly upstream of their target transcription factors.
As time is an important variable when considering crosstalk events, we propose to build
a computational model of the dynamics of the two pathways.
Such an \emph{in silico} model should allow us to identify the key interactions in the crosstalk.
Thanks to the model, we will be able to refine our current
knowledge on the studied network by identifying specifically targeted laboratory experiments.

\begin{table}[htbp]
\centering
\begin{tabular}{|l||l|l|lcl|}
\hline%
%     & 10 ng/ml IL-1$\beta$ & 75 ng/ml Wnt-3a & 10 ng/ml IL-1$\beta$ + \\
%     & & & 75 ng/ml Wnt-3a \\
&\multicolumn{1}{|c|}{IL-1$\beta$}&\multicolumn{1}{|c|}{Wnt-3a}&\multicolumn{1}{|c}{IL-1$\beta$}&\hspace{-5mm}+\hspace{-5mm}&\multicolumn{1}{c|}{\hspace{-5mm}Wnt-3a}\\[-1ex]%
&\multicolumn{1}{|c|}{\scriptsize10 ng/ml}&\multicolumn{1}{|c|}{\scriptsize75 ng/ml}&\multicolumn{1}{|c}{\scriptsize10 ng/ml}&{}&\multicolumn{1}{c|}{\hspace{-5mm}\scriptsize75 ng/ml}  \\
\hline
\hline
  IL-1$\beta$ & $+++$ & $-$ & $++$ & & \\
\hline
  Axin & $-$ & $++$ & $+$ & & \\
\hline
%  ID1 & $+$ & $++$ & $+$ & & \\
% \hline
  Sox9 & $+$ & $-$ & $-$ & & \\
\hline
  ColIIa & $-$ & $-/+$ & $-$ & & \\
\hline
\end{tabular}
\caption{The effects of treatments with IL-1$\beta$ and Wnt-3a on the expression of some proteins
in human knee chondrocytes. Effects were measured
as n-fold variations with respect to the initial concentrations, and are represented in the table as follows:
$+$ under 10 times increase; $++$ more than 10 but less than 100 times increase;
$+++$ more than 100 times increase. Similarly, $-$ means less than 10 times decrease.
We use $-/+$ in one case to indicate that treatment with Wnt-3a causes
an initial decrease ($\sim{}0.5$-fold) followed by an increase ($\sim{}2$-fold) in the production of ColIIa. \label{tab:pcr-effects}}
\end{table}
